---
title: 'Effect and Flavor of the 3 Different Type of Cannabis Analysis'
author: "Chengran (Owen) Ouyang"
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: true
    fig_caption: true
    toc: true
    fig_width: 7
    fig_height: 4.5
    theme: cosmo
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


******

# Introduction

******


<img src="https://images.unsplash.com/photo-1518589259587-1566f6ccd972?ixlib=rb-0.3.5&ixid=eyJhcHBfaWQiOjEyMDd9&s=f1342e3f0f84c52580e73c607ae29f6a&auto=format&fit=crop&w=1868&q=80">


**Objectives:** The goal of this kernel is to analyze the effect and flavor of 3 different type of Cannabis.


EDA includes datatable, skim, 3D plotly, DrillDown and NLP.


If you have any question, please leave a comment and if you like the kernel, please give me an upvote~ Thanks!


******
# Basic Set up{.tabset .tabset-fade .tabset-pills}
******


******

## Load Packages

******


```{r  message=FALSE, warning=FALSE}
library(tidyverse)
library(skimr)
library(highcharter)
# library(qdap)
library(tm)
library(plotly)
library(viridis)
library(wordcloud)
library(plotrix)
library(DescTools)
library(DT)
library(ggraph)
library(igraph)
library(ggthemes)
library(visNetwork)
```


******
## Load Dataset
******


```{r  message=FALSE, warning=FALSE}
weed <- read_csv("input/cannabis.csv")
```


******
# Glimpses{.tabset .tabset-fade .tabset-pills}
******


******
## skim
******


```{r  message=FALSE, warning=FALSE}
weed %>% skim() %>% kable()
```


******
## datatable
******


```{r  message=FALSE, warning=FALSE}
weed %>% 
  datatable(filter = 'top', options = list(
  pageLength = 15, autoWidth = TRUE

))
```


******
## glimpse
******


```{r  message=FALSE, warning=FALSE}
weed %>% glimpse()
```


******
# Cannabis Ranking Distribution
******


```{r  message=FALSE, warning=FALSE}
weed$Rating %>% PlotFdist("Cannabis Ranking Distribution")
```


******
# TreeMaps{.tabset .tabset-fade .tabset-pills}
******


******
## TreeMap by Type
******


```{r  message=FALSE, warning=FALSE}
by_type <- weed %>% 
  count(Type)
hchart(by_type, type = 'treemap', hcaes(x = 'Type', value = 'n', color = 'n'))

rm(by_type)
```


******
## TreeMap by Effects
******


```{r  message=FALSE, warning=FALSE}
weed_effects <- weed %>% 
  mutate(Effects = str_split(Effects,',')) %>% 
  unnest(Effects)


weed_effects %>% 
  count(Effects) %>% 
  hchart(type = 'treemap', hcaes(x = 'Effects', value = 'n', color = 'n'))
```


******
## TreeMap by Flavors
******


```{r  message=FALSE, warning=FALSE}
weed_flavor <- weed %>% 
  filter(Flavor != 'none') %>% 
  mutate(Flavor = str_split(Flavor, ',')) %>% 
  unnest(Flavor)


weed_flavor %>% 
  count(Flavor) %>% 
  hchart(type = 'treemap', hcaes(x = 'Flavor', value = 'n', color = 'n'))
```


******
# Interactive Drill Down Graph for 3 Types by Effects 
******

**Click the part to Drill Down!**


```{r  message=FALSE, warning=FALSE}
df1 <- weed %>% 
  group_by(name = Type, drilldown = Type) %>% 
  summarise(y = n()) %>% 
  arrange(desc(y))

df2 <- weed_effects %>% 
  group_by(Type, Effects) %>% 
  mutate(y = n()
         # , colorByPoint =  1
         ) %>% 
  arrange(desc(y)) %>%
  group_by(name = Type, id = Type
           # , colorByPoint
           ) %>% 
  do(data = list_parse(
    mutate(.,name = Effects, drilldown = tolower(paste(Type, Effects,sep=": "))) %>% 
      group_by(name, drilldown) %>% 
      summarise(y=n()) %>% 
      select(name, y, drilldown) %>%
      arrange(desc(y)))) 

a <- highchart() %>% 
  hc_chart(type = 'pie') %>% 
  hc_xAxis(type = "category") %>% 
  hc_add_series(name = 'number of cannabis', data = df1, colorByPoint = 1) %>% 
  hc_drilldown(
    allowPointDrilldown = TRUE,
    series =list_parse(df2)
  ) %>%
  hc_legend(enabled = F) %>% 
  hc_title(text = "Type of Cannbis vs Effects Pie Chart") %>% 
  hc_add_theme(hc_theme_darkunica())

b <- highchart() %>% 
  hc_chart(type = 'bar') %>% 
  hc_xAxis(type = "category") %>% 
  hc_add_series(name = 'number of cannabis', data = df1, colorByPoint = 1) %>% 
  hc_drilldown(
    allowPointDrilldown = TRUE,
    series =list_parse(df2)
  ) %>%
  hc_legend(enabled = F) %>% 
  hc_title(text = "Type of Cannbis vs Effects Bar Chart") %>% 
  hc_add_theme(hc_theme_darkunica())
rm(df1, df2)



lst <- list(
  a,
  b
)



hw_grid(lst, rowheight = 400)
rm(a, b, lst)
```

******
# Interactive Drill Down Graph for 3 Types by Flavors 
******


**Click the part to Drill Down!**


```{r  message=FALSE, warning=FALSE}
df1 <- weed %>% 
  group_by(name = Type, drilldown = Type) %>% 
  summarise(y = n()) %>% 
  arrange(desc(y))

df2 <- weed_flavor %>% 
  group_by(Type, Flavor) %>% 
  mutate(y = n(), colorByPoint = 1) %>% 
  arrange(desc(y)) %>%
  group_by(name = Type, id = Type
           # , colorByPoint
           ) %>% 
  do(data = list_parse(
    mutate(., name = Flavor, drilldown = tolower(paste(Type, Flavor,sep=": "))) %>% 
      group_by(name, drilldown) %>% 
      summarise(y=n()) %>% 
      select(name, y, drilldown) %>%
      arrange(desc(y)))) 

a <- highchart() %>% 
  hc_chart(type = 'pie') %>% 
  hc_xAxis(type = "category") %>% 
  hc_add_series(name = 'number of cannabis', data = df1
                # , colorByPoint = 1
                ) %>% 
  hc_drilldown(
    allowPointDrilldown = TRUE,
    series =list_parse(df2)
  ) %>%
  hc_legend(enabled = F) %>% 
  hc_title(text = "Type of Cannbis vs Flavor Pie Chart") %>% 
  hc_add_theme(hc_theme_darkunica())


b <- highchart() %>% 
  hc_chart(type = 'bar') %>% 
  hc_xAxis(type = "category") %>% 
  hc_add_series(name = 'number of cannabis', data = df1, colorByPoint = 1) %>% 
  hc_drilldown(
    allowPointDrilldown = TRUE,
    series =list_parse(df2)
  ) %>%
  hc_legend(enabled = F) %>% 
  hc_title(text = "Type of Cannbis vs Flavor Bar Chart") %>% 
  hc_add_theme(hc_theme_darkunica())
rm(df1, df2)



lst <- list(
  a,
  b
)



hw_grid(lst, rowheight = 400)
rm(a, b, lst)
```


******
# NLP Setup{.tabset .tabset-fade .tabset-pills}
******


******
## clean corpus
******


```{r  message=FALSE, warning=FALSE}
# clean corpus
cleanCorpus <- function(corpus){
  
  corpus.tmp <- tm_map(corpus, removePunctuation)
  corpus.tmp <- tm_map(corpus.tmp, stripWhitespace)
  corpus.tmp <- tm_map(corpus.tmp, content_transformer(tolower))
  v_stopwords <- c(stopwords("en"), c("thats","weve","hes","theres","ive","im",
                                      "will","can","cant","dont","youve","us",
                                      "youre","youll","theyre","whats","didnt"))
  corpus.tmp <- tm_map(corpus.tmp, removeWords, v_stopwords)
  corpus.tmp <- tm_map(corpus.tmp, removeNumbers)
  return(corpus.tmp)
}

```

******
## frequent terms 
******


```{r  message=FALSE, warning=FALSE}
# frequent terms 
frequentTerms <- function(text){
  
  s.cor <- Corpus(VectorSource(text))
  s.cor.cl <- cleanCorpus(s.cor)
  s.tdm <- TermDocumentMatrix(s.cor.cl)
  s.tdm <- removeSparseTerms(s.tdm, 0.999)
  m <- as.matrix(s.tdm)
  word_freqs <- sort(rowSums(m), decreasing=TRUE)
  dm <- data.frame(word=names(word_freqs), freq=word_freqs)
  return(dm)
  
}
```


******
## clean by each type
******


```{r  message=FALSE, warning=FALSE}
# clean by each Type
clean_top_char <- function(dataset){
  all_dialogue <- list()
  namelist <- list()
  
  for (i in 1:3){
    top <- dataset %>% count(Type) %>% arrange(desc(n)) %>% head(20)
    name <- top$Type[i]
    Description <- paste(dataset$Description[dataset$Type == name], collapse = " ")
    all_dialogue <- c(all_dialogue, Description)
    namelist <- c(namelist, name)
    
  }
  
  
  
  all_clean <- all_dialogue %>% 
    VectorSource() %>% 
    Corpus() %>% 
    cleanCorpus() %>% 
    TermDocumentMatrix() %>%
    as.matrix()
  
  colnames(all_clean) <- namelist
  
  assign("all_clean",all_clean,.GlobalEnv)
  all_clean %>% head()
}

weed %>% clean_top_char()
```


******
# Top 30 Words in Description
******


```{r  message=FALSE, warning=FALSE}
weed$Description %>% 
  frequentTerms() %>% 
  # dim()
  head(30) %>% 
  mutate(word = factor(word))%>% 
  plot_ly(x = ~reorder(word,-freq), y = ~freq, colors = viridis(10)) %>%
  add_bars(color = ~word) %>%
  layout(title = "Top 30 Words", 
         yaxis = list(title = " "), 
         xaxis = list(title = ""), 
         margin = list(l = 100))
```


******
# WordCloud{.tabset .tabset-fade .tabset-pills}
******


******
## Commonality Cloud
******


**Sativa vs Indica**


```{r  message=FALSE, warning=FALSE}
commonality.cloud(all_clean[,c("sativa","indica")], colors = "steelblue1", at.least = 2, max.words = 100)

```


******
## Comparison Cloud
******


**Sativa vs Indica**


```{r  message=FALSE, warning=FALSE}
comparison.cloud(all_clean[,c("sativa","indica")], colors = c("#F8766D", "#00BFC4"), max.words=50)
```


******
# Pramid Plot
******


**Sativa vs Indica**


```{r  message=FALSE, warning=FALSE}
common_words <- all_clean %>%
  as.data.frame() %>% 
  rownames_to_column() %>% 
  filter(sativa>0, indica>0) %>% 
  # select(sativa, indica)
  mutate(difference = abs(sativa - indica)) %>% 
  arrange(desc(difference)) 

common_words_25 <- common_words%>%
  head(25)

pyramid.plot(common_words_25$sativa, common_words_25$indica,
             labels = common_words_25$rowname, gap = 200,
             top.labels = c("sativa", "Words", "indica"),
             main = "Words in Common", laxlab = NULL, 
             raxlab = NULL, unit = NULL)
rm(common_words, common_words_25)
```


******
# 3D Plotly
******


```{r  message=FALSE, warning=FALSE}
effects <- weed_effects$Effects %>% unique() %>% tolower()
rm(weed_effects)


effectByType <- all_clean %>%
  as.data.frame() %>% 
  rownames_to_column('word') %>% 
  filter(word %in% effects) %>% 
  mutate(word=factor(word))
  

effectByType %>% 
  plot_ly(x=~hybrid,y=~sativa,z= ~indica, color=~word, hoverinfo = 'text', colors = viridis(15),
          text = ~paste('Effects:', word,
                        '<br>hybrid:', hybrid,
                        '<br>sativa:', sativa,
                        '<br>indica:', indica)) %>% 
  add_markers(opacity = 0.8) %>%
  layout(title = "Effects by Different Cannabis",
         annotations=list(yref='paper',xref="paper",y=1.05,x=1.1, text="Effects",showarrow=F),
         scene = list(xaxis = list(title = 'hybrid'),
                      yaxis = list(title = 'sativa'),
                      zaxis = list(title = 'indica')))
```


******
# Hybrid Network 1
******


```{r  message=FALSE, warning=FALSE}
effectByType %>%
  mutate(type = 'hybrid') %>%
  select(word, type, hybrid) %>% 
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = hybrid), show.legend = FALSE) +
  geom_node_point(color = "firebrick", size = 20, alpha = .5) +
  geom_node_text(aes(label = name), col = "white") +
  theme_solarized(light = F)
```


******
# Hybrid Netword 2
******


```{r  message=FALSE, warning=FALSE}
network3_edg <- effectByType %>% 
  mutate(type = 'hybrid') %>%
  select(word, type, hybrid) %>% 
  filter(hybrid>0) %>% 
  rename(from = type, to = word, weight = hybrid, width = hybrid)

network3_node <- effectByType %>% 
  mutate(type = 'hybrid') %>%
  filter(hybrid>0) %>% 
  select(word, hybrid) %>% 
  rename(id = word, size = hybrid)
network3_node$label <- network3_node$id # Node label

network3_node <- bind_rows(network3_node,data.frame(id = 'hybrid',  size = 24,  label = 'hybrid'))

visNetwork(network3_node, network3_edg, height = "500px", width = "100%") %>% 
  visIgraphLayout(layout = "layout_with_lgl") %>% 
  visEdges(shadow = TRUE,
           color = list(color = "gray", highlight = "orange"))
```


******
# Hybrid Netword 3
******


```{r  message=FALSE, warning=FALSE}
network3_edg <- effectByType %>% 
  mutate(type = 'hybrid') %>%
  select(word, type, hybrid) %>% 
  filter(hybrid>0) %>% 
  rename(from = type, to = word)

network3_node <- effectByType %>% 
  mutate(type = 'hybrid') %>%
  filter(hybrid>0) %>% 
  select(word) %>% 
  rename(id = word)
network3_node$label <- network3_node$id # Node label

network3_node <- bind_rows(network3_node,data.frame(id = 'hybrid', label = 'hybrid'))

visNetwork(network3_node, network3_edg, height = "500px", width = "100%") %>% 
  # visIgraphLayout(layout = "layout_with_lgl") %>% 
  visEdges(shadow = TRUE,
           color = list(color = "gray", highlight = "orange"))
```




******
# Conclusion
******


Hope you enjoyed the kernel and don't forget to upvote~ Thanks a lot!

